Dual selection games

### 2018-07-09 articles/dual-selection-games/article.tex
start adding perfect info results

\begin{definition}
  The set \(\mc A'\) is said to be a \term{reflection} of the set \(\mc A\)
  if \[\{\ran f:f\in\mathbf C(\mc A')\}=\mc A.\]
\end{definition}

@@

\begin{theorem}
  Let \(\mc A'\) be a reflection of \(\mc A\).

  Then
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(\sigma(n)\in\mc A\), \(\sigma(n)=\ran{f_n}\)
  for some \(f_n\in\mathbf C(\mc A')\). So let
  \(\tau(A,n)=f_n(A)\) for all \(A\in \mc A'\) and \(n<\omega\).
  Suppose \(A_n\in \mc A'\) for all \(n<\omega\).
  Note that since \(\sigma\) is winning and 
  \(\tau(A_n,n)=f_n(A_n)\in\ran{f_n}=\sigma(n)\),
  \(\{\tau(A_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).
  Let \(f_n\in\mathbf C(\mc A')\) be defined by \(f_n(A)=\sigma(A,n)\).
  Since \(\mc A=\{\ran f:f\in\mathbf C(\mc A')\}\), let
  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
  all \(n<\omega\). Choose \(A_n\in\mc A'\) such that 
  \(B_n=f_n(A_n)=\sigma(A_n,n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

>>>>

\begin{definition}
  The set \(\mc R\) is said to be a \term{reflection} of the set \(\mc A\)
  if \[\mc A= \{\ran f:f\in\mathbf C(\mc R)\}.\]
\end{definition}

@@

\begin{lemma}
  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
\end{lemma}
\begin{proof}
  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).

  Likewise if \(x\in\bigcup\mc R\), so \(x\in R\) for some \(R\in \mc R\).
  Let \(f\in\mathbf C(\mc R)\) satisfy \(f(R)=x\), so \(x\in\ran{f}\),
  showing \(x\in\bigcup\mc A\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\).

  Then
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(\sigma(n)\in\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\), 
  \(\sigma(n)=\ran{f_n}\)
  for some \(f_n\in\mathbf C(\mc R)\). So let
  \(\tau(R,n)=f_n(R)\) for all \(R\in \mc R\) and \(n<\omega\).
  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
  Note that since \(\sigma\) is winning and 
  \(\tau(R_n,n)=f_n(R_n)\in\ran{f_n}=\sigma(n)\),
  \(\{\tau(R_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\).
  Since \(\tau(n)\in\mc A=\{\ran f:f\in\mathbf C(\mc R)\}\), let
  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\).

  Then
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
  Let \(n<\omega\). Suppose that for each \(R\in\mc R\),
  there was \(g(R)\in R\) such that for all \(A\in \mc A\),
  \(\sigma(A,n)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\),
  and \(\sigma(\ran g,n)\not=g(R)\) for all \(R\in\mc R\),
  a contradiction.

  So choose \(\tau(n)\in\mc R\) such that for all \(r\in \tau(n)\)
  there exists \(A_{r,n}\in\mc A\) such that \(\sigma(A_{r,n},n)=r\).
  It follows that when \(r_n\in\tau(n)\) for \(n<\omega\),
  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n,n}:n<\omega\}\in B\),
  so \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Then \(\sigma(n)\in\mc R\), so for \(A\in\mc A\), let
  \(f_A\in\mathbf C(\mc R)\) satisfy \(A=\ran{f_A}\),
  and let \(\tau(A,n)=f_A(\sigma(n))\).
  Then if \(A_n\in\mc A\) for \(n<\omega\), \(\tau(A_n,n)\in\sigma(n)\),
  so \(\{\tau(A_n,n):n<\omega\}\in\mc B\).
  Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\).

  Then
  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\).
  Let \(c(\emptyset)=\emptyset\). Suppose 
  \(c(s)\in(\bigcup A)^{<\omega}=(\bigcup R)^{<\omega}\)
  is defined for \(s\in\mc R^{<\omega}\). Since \(\sigma(c(s))\in\mc A\),
  let \(f_s\in\mathbf C(\mc R)\) satisfy \(\sigma(c(s))=\ran{f_s}\),
  and let \(c(s\concat\<R\>)=c(s)\concat\<f_s(R)\>\).
  Then let \(c(\alpha)=\bigcup\{c(\alpha\rest n):n<\omega\}\)
  for \(\alpha\in\mc R^\omega\), so
  \[
    c(\alpha)(n)
      =
    f_{\alpha\rest n}(\alpha(n))
      \in
    \ran{f_{\alpha\rest n}}
      =
    \sigma(c(\alpha\rest n))
  \]
  demonstrating that \(c(\alpha)\) is a legal attack against \(\sigma\).

  Let \(\tau(s\concat\<R\>)=f_s(R)\). Consider the attack \(\alpha\in\mc R^\omega\)
  against \(\tau\). Then since \(\sigma\) is winning and
  \(
    \tau(\alpha\rest n+1)=f_{\alpha\rest n}(\alpha(n))\in
    \ran{f_{\alpha\rest n}}=\sigma(c(\alpha\rest n))
  \), it follows that \(\{\tau(\alpha\rest n+1):n<\omega\}\not\in\mc B\).
  Thus \(\tau\) witnesses
  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).

%  Now let \(\sigma\) witness
%  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
%  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\).
%  Since \(\tau(n)\in\mc A=\{\ran f:f\in\mathbf C(\mc R)\}\), let
%  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
%  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
%  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
%  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
%  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}
